To be FAIR: Theory Specification Needs an Update

### 2025-02-26 manuscript.Rmd
Update manuscript.Rmd

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1"
    corresponding: yes
    address: "Professor Cobbenhagenlaan 125, 5037 DB Tilburg, The Netherlands"
    email: "c.j.vanlissa@tilburguniversity.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Formal Analysis
      - Funding acquisition
      - Methodology
      - Project administration
      - Software
      - Supervision
      - Writing – original draft
      - Writing – review & editing
  - name: "Aaron Peikert"
    affiliation: "2,3"
    role:
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
  - name: "Andreas M. Brandmaier"
    affiliation: "2,3,4"
    role:
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
  - name: "Felix D. Schönbrodt"
    affiliation: "5"
    role:
      - Conceptualization
      - Writing – review & editing
  - name: "Noah N.N. van Dongen"
    affiliation: "6"
    role:
      - Writing – review & editing
  - name: "Maximilian S. Ernst"
    affiliation: "2,7"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Writing – review & editing
      - Investigation
affiliation:
  - id            : "1"
    institution   : "Tilburg University, dept. Methodology & Statistics"
  - id            : "2"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "3"
    institution   : "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany"
  - id            : "4"
    institution   : "Department of Psychology, MSB Medical School Berlin, Berlin, Germany"
  - id            : "5"
    institution   : "Ludwig-Maximilians-Universität München, Germany"
  - id            : "6"
    institution   : "University of Amsterdam, the Netherlands"
  - id            : "7"
    institution   : "Max Planck School of Cognition, Leipzig, Germany"
authornote: |
  This is a preprint paper, generated from Git Commit # `r substr(gert::git_commit_id(),1,8)`.

>>>>

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1"
    corresponding: yes
    address: "Professor Cobbenhagenlaan 125, 5037 DB Tilburg, The Netherlands"
    email: "c.j.vanlissa@tilburguniversity.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Formal Analysis
      - Funding acquisition
      - Methodology
      - Project administration
      - Software
      - Supervision
      - Writing – original draft
      - Writing – review & editing
  - name: "Aaron Peikert"
    affiliation: "2,3"
    role:
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
  - name: "Andreas M. Brandmaier"
    affiliation: "2,3,4"
    role:
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
  - name: "Felix D. Schönbrodt"
    affiliation: "5"
    role:
      - Conceptualization
      - Writing – review & editing
  - name: "Noah N.N. van Dongen"
    affiliation: "6"
    role:
      - Writing – review & editing
  - name: "Maximilian S. Ernst"
    affiliation: "2,7"
    role:
      - Writing – review & editing
      - Investigation
affiliation:
  - id            : "1"
    institution   : "Tilburg University, dept. Methodology & Statistics"
  - id            : "2"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "3"
    institution   : "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany"
  - id            : "4"
    institution   : "Department of Psychology, MSB Medical School Berlin, Berlin, Germany"
  - id            : "5"
    institution   : "Ludwig-Maximilians-Universität München, Germany"
  - id            : "6"
    institution   : "University of Amsterdam, the Netherlands"
  - id            : "7"
    institution   : "Max Planck School of Cognition, Leipzig, Germany"
authornote: |
  This is a preprint paper, generated from Git Commit # `r substr(gert::git_commit_id(),1,8)`.
